Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-22 edubots_surveys.Rnw
Correct and expand biblio
And add justification for finding out the needs of the user #48

Several higher education chatbots' evaluation studies have been undertaken. For
instance, a recent evaluation review study presented by Smutny and Schreiberova
\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
Messenger with the focus to identify characteristics and quality metrics such as
language, subject matter and platform\textcolor{blue}{, whereas the study undertaken by Pérez and collaborators
\cite{perez2020rediscovering} aimed to categorise educational chatbots, according
to their, purpose into service-oriented and teaching-oriented}. The first category
includes those that provide service support such as the chatbot Ask Holly
\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
students' questions about enrolment and registration. Ask L. U.
\cite{LancasterUniversity_2019} answers students' frequently asked questions
about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
and Differ \cite{differ.chat} facilitate breaking the ice between new students
by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
proposed a generic chatbot for university students that is able to answer to
their frequently asked questions.  For some time, the University of Granada had
ELVIRA as a chatbot in its main web page \cite{MOREO20129}. Besides being able
to answer pre-established (frequent) questions, it did so from the website of
the University of Granada using an inset character, voiced by a real person, who
lip-synced the answers. The emphasis in the case of Elvira, however, was on the
authenticity of the synchronization more than in making the update of questions
and answers simpler, or more interactive, using actual messaging platforms.  In
most cases, using the inset search engine was able to give you more up-to-date
and accurate answers than the ones provided by ELVIRA, which had to be updated
by hand (and not too often).

@@

Despite its (arguably) successful implementation in different higher education
institutions, over all in the fringes of educational activity, not in the actual
interaction student-teacher, its implementation or deployment is not trivial.
Some authors, for instance \cite{sjostrom2018designing} have proposed a
conceptual architecture for the adoption of teaching-oriented chatbots in higher
education.  This conceptual architecture is based on a systematic literature
review of previous studies, examining the design of chatbots in higher
education, as well as making a content analysis of student emails and discussion
forum posts of four instances of a Java programming course.  The study outlined
several design considerations; among them, the authors emphasised the importance
of developing chatbots in platforms that students and educators are familiar
with and can easily access (i.e. Facebook Messenger) which was confirmed with
\cite{hobert2019you} and \cite{fernoagua2018intelligent} studies. In addition,
Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} argued that a
conceptualisation of learners' questions could aid designers in integrating the
appropriate types of questions that the chatbots should support for different
courses.  Coronado et al. \cite{coronado2018cognitive} proposed agents that
store learning materials to be provided on demand to students, whereas the
authors in \cite{crockett2017predicting} reported on tutoring systems, which can
perform initial assessments of students' understanding and provide learning
material that would advance their understanding to the next level.

Regarding the factors for the adoption of chatbots in higher education, many
studies have focused on the evaluation of technology acceptance and usability
\cite{Roblyer2010,Pimmer2019}. However, higher education is a special domain
where, according to Hobert \cite{hobert2019you}, specific pedagogical factors
such as learning success and increased motivation are more important.  Therefore,
to develop \textcolor{blue}{effective} chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) needs should be carefully
collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}.

>>>>

Several higher education chatbots' evaluation studies have been undertaken. For
instance, a recent evaluation review study presented by Smutny and Schreiberova
\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
Messenger with the focus to identify characteristics and quality metrics such as
language, subject matter and platform\textcolor{blue}{, whereas the study undertaken by Pérez and collaborators
\cite{perez2020rediscovering} aimed to categorise educational chatbots, according
to their, purpose into service-oriented and teaching-oriented}. The first category
includes those that provide service support such as the chatbot Ask Holly
\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
students' questions about enrolment and registration. Ask L. U.
\cite{LancasterUniversity_2019} answers students' frequently asked questions
about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
and Differ \cite{differ.chat} facilitate breaking the ice between new students
by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
proposed a generic chatbot for university students that is able to answer to
their frequently asked questions \textcolor{blue}{and, for some time, the University of Granada had
\textcolor{blue}{Elvira} as a chatbot in its main web page \cite{MOREO20129} to perform that duty.} Besides being able
to answer pre-established (frequent) questions, it did so from the website of
the University of Granada using an inset \textcolor{blue}{persona, voiced by a real person, who
lip-synced the answers. The emphasis in the case of Elvira, however, was on the
authenticity of the synchronization more than in making the update of questions
answered simpler, or more interactive, or more open to the rest of the university staff, using actual messaging platforms.  In
most cases, using the embedded search engine was able to give you more up-to-date
and accurate answers than the ones provided by Elvira, which had to be updated
by hand (and not too often). It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide an useful service. Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in an university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, something which is the focus of this paper}.

@@

Despite its (arguably) successful implementation in different higher education
institutions, over all in the fringes of educational activity, not in the actual
interaction student-teacher, its implementation or deployment is not trivial.
Some authors, for instance \cite{sjostrom2018designing} have proposed a
conceptual architecture for the adoption of teaching-oriented chatbots in higher
education.  This conceptual architecture is based on a systematic literature
review of previous studies, examining the design of chatbots in higher
education, as well as making a content analysis of student emails and discussion
forum posts of four instances of a Java programming course.  The study outlined
several design considerations; among them, the authors emphasised the importance
of developing chatbots in platforms that students and educators are familiar
with and can easily access (i.e. Facebook Messenger) which was confirmed with
\cite{hobert2019you} and \cite{fernoagua2018intelligent} studies. In addition, \cite{sjostrom2018designing} argued that a
conceptualisation of learners' questions could aid designers in integrating the
appropriate types of questions that the chatbots should support for different
courses.  \textcolor{blue}{Some other authors}, like \cite{coronado2018cognitive}, proposed agents that
store learning materials to be provided on demand to students, whereas the
authors in \cite{crockett2017predicting} reported on tutoring systems, which can
perform initial assessments of students' understanding and provide learning
material that would advance their understanding to the next level.

Regarding the factors for the adoption of chatbots in higher education, many
studies have focused on the evaluation of technology acceptance and usability
\cite{Roblyer2010,Pimmer2019}. However, higher education is a special domain
where, according to Hobert \cite{hobert2019you}, specific pedagogical factors
such as learning success and increased motivation are more important.  Therefore,
to develop \textcolor{blue}{effective chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) needs should be carefully
collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}. These needs include, but are not limited to, student's learning success due to higher motivation, but these are a posteriori effects that cannot be assessed in advance; this is why we focus in this paper on what the teachers are looking for in a TAM and associated technologies like chatbots; both authors focus on what the teachers need in terms of the latter; this paper will focus on a wider perspective trying to ascertain what they are looking for in terms of general messaging technology. The classical literature \cite{tam91} already proposes that any adoption of technology must be tuned in to the user needs and experience. In this paper we will try to find out what those are in order to propose a successful model of adoption of chatbot technology}.
